DataGatheringandAnalysis

### 2014-11-10 GEMDataSource.Rmd
Deleted unecessary header
Imported, cleaned, and merged GEM data

### Import data from GEM Survey ###

# Import fear of failure data
FearFail <- repmiss::source_data("", 
```

>>>>

# Library Repmis, Tidy, Reshape2, and plyr packages
library(repmis)
library(tidyr)
library(reshape2)
library(plyr)

#### Import data from GEM Survey ####

# Import fear of failure data
FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = TRUE)

# Import current owner data
CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = TRUE)

# Import entrepreneurial intention data
EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = TRUE)

# Import nascent entrepreneur data
NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = TRUE)

# Import perceived capabilities data
PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = TRUE)

#### Clean data using tidy ####

### Clean FearFail ###

# Remove X's in FearFail year columns
names(FearFail) <- gsub("X", "", names(FearFail))

# Change years from columns to rows and create CFearFail
CFearFail <- melt(data = FearFail,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CFearFail <- plyr::rename(x = CFearFail, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Fear"))

### Clean CurrentOwner ###
# Remove X's in CurrentOwner year columns
names(CurrentOwner) <- gsub("X", "", names(CurrentOwner))

# Change years from columns to rows and create CCurrentOwner
CCurrentOwner <- melt(data = CurrentOwner,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CCurrentOwner <- plyr::rename(x = CCurrentOwner, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Owner"))

### Clean EntreIntention ###
# Remove X's in EntreIntention year columns
names(EntreIntention) <- gsub("X", "", names(EntreIntention))

# Change years from columns to rows and create CEntreIntention (No 2001 data available)
CEntreIntention <- melt(data = EntreIntention,
                  id.vars = c("Country"),
                  measure.vars = c("2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CEntreIntention <- plyr::rename(x = CEntreIntention, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Intention"))

### Clean NascentEntre ###
# Remove X's in NascentEntre year columns
names(NascentEntre) <- gsub("X", "", names(NascentEntre))

# Change years from columns to rows and create CNascentEntre
CNascentEntre <- melt(data = NascentEntre,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CNascentEntre <- plyr::rename(x = CNascentEntre, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Nascent"))

### Clean PerceivedCapabilities ###
# Remove X's in PerceivedCapabilities year columns
names(PerceivedCapabilities) <- gsub("X", "", names(PerceivedCapabilities))

# Change years from columns to rows and create CPreceivedCapabilities
CPerceivedCapabilities<- melt(data = PerceivedCapabilities,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
                                      replace = c("variable" = "Year",
                                                  "value" = "Percent Perceived"))

# Merge the data
MergedGEM <- merge(CCurrentOwner, CEntreIntention,
                   union("Country", "Year"),
                   all = TRUE)

MergedGem2 <- merge(CFearFail, CNascentEntre,
                   union("Country", "Year"),
                   all = TRUE)

MergedGem3 <- merge(CPerceivedCapabilities, MergedGEM,
                   union("Country", "Year"),
                   all = TRUE)

FinalMerge <- merge(MergedGem2, MergedGem3,
                   union("Country", "Year"),
                   all = TRUE)

```
